Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-05-24 analysis/preregistration_template.Rmd
Incorporate @LibbyR's changes #10
Add @LibbyR 's changes to raw Rmd instead of to .md file.

*Specifies the decision-making context in which the model will be used, the clients driving model development or stakeholders addressed by the model. It also includes specification of model outputs, statements of the domain of applicability of the model, as well as the extent by which model outputs may be acceptably extrapolated (Grimm et al. 2014).*

@@

## 1.3.1 Explain analytical objectives

>>>>

*Specifies the decision-making context in which the model will be used. Important components include the decision maker and stakeholders (including experts) and their view on: i) the nature of the problem or decision addressed and how the scope of the modelling tool fits within the (broader) context (i.e. model purpose; ii) the relevant spatial and temporal scales relevant to the decision context; iii) specified desired outputs; iv) role and inclusion in model development and testing; v) whether they forsee unnacceptable outcomes that need to be represented in the model (i.e. as constraints), and; vi) what future scenarios does the model need to account for (noting this may be revised later).  It should also provide a summary of the domain of applicability of the model, and reasonable extrapolation limits (Grimm et al. 2014).*

@@

## 1.3.1 Explain analytical objectives (MAKE THIS A SEPARATE SECTION WHICH INCLUDES PERF MEASURES)
